---
title: "Results testing"
author: "Leonardo Souto Ferreira"
date: today
format: pdf
geometry:
  - margin=2cm
warning: false
message: false
echo: false
fig-width: 8
fig-height: 6
execute:
  enabled: false
---

::: {.callout-note}
Code execution is disabled for this document (`execute: enabled: false`):
it reads `results/aggregated/combined_results_<RUN_ID>_refined_second.csv`,
the aggregated output of one specific past fitting run, which isn't part of
this repository and only exists on the machine/cluster that produced it.
Render it on its own (`quarto render vignettes/create_profile_grids.qmd
--execute`) once you have a matching results file and have updated the
hard-coded `RUN_ID` below.
:::




```{r, fig.width = 8, fig.height = 6, message = FALSE}
proj_root <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
setwd(proj_root)
knitr::opts_knit$set(root.dir = proj_root)
pkgload::load_all(proj_root)
library(tidyverse)
library(rstatix)


compute_parameter_boundaries <- function(
  dataset, diff_LL,
  ignore_param = NULL, remove_outliers = TRUE
) {
  dataset <- dataset |>
    filter(loglik >= max(loglik) - diff_LL)
  outlier_list <- dataset |>
    filter(loglik >= max(loglik) - diff_LL) |>
    select(-any_of(c("loglik.se", "sample", "flag", "loglik", ignore_param))) |>
    mutate(id = seq(1, nrow(dataset), 1)) |> # To create a unique column required to make that data in long form
    pivot_longer(-id) |> # To make the data in long form required for `tidyverse`
    group_by(name) |> # Based on which column you want aggregate
    identify_outliers(value) |>
    select(id, is.outlier) |>
    distinct_all() |>
    arrange(desc(id))

  bounds <- dataset |>
    mutate(id = seq(1, nrow(dataset), 1)) |>
    left_join(outlier_list) |>
    replace_na(list(is.outlier = FALSE)) |>
    filter(!is.outlier) |>
    select(-any_of(c("loglik.se", "sample", "flag", "loglik", ignore_param))) |>
    pivot_longer(everything(), names_to = "parameter") |>
    group_by(parameter) |>
    summarize(
      min_val = min(value, na.rm = TRUE),
      max_val = max(value, na.rm = TRUE)
    )

  return(bounds)
}

generate_grid <- function(dataset, k = 1, diff_LL = 10, n_splits = 100, reps = 100, write = TRUE, output_dir = NULL) {
  if (!dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
  }
  bounds <- dataset |> compute_parameter_boundaries(diff_LL = diff_LL, ignore_param = "delta")
  params <- dataset |>
    get_top_sample(k = k)
  param_grid <- params |>
    lapply(rep, n_splits * reps) |>
    bind_cols()
  grids <- bounds |>
    apply(1, function(x) {
      param <- x |> unlist()
      param <- param[1]
      min_val <- x[2] |> as.numeric()
      max_val <- x[3] |> as.numeric()
      df <- param_grid |> mutate("{param}" := (seq(min_val, max_val, length.out = n_splits) |> rep(each = reps)))
      if (write) {
        write_csv(df, file.path(output_dir, paste0("param_grid_", param, ".csv")))
      }
      return(df)
    })

  names(grids) <- bounds |> pull("parameter")

  return(grids)
}


```

## Ahmedabad

### hadISD

#### RH
```{r}
result <- clean_file_result("results/aggregated/combined_results_20260204T181902Z_04eb_refined_second.csv") |>
  filter(rho >= 0.01, alpha < 1) |>
  filter(loglik >= max(loglik) - 40)

params <- get_top_sample(result)
print(params)

outlier_list <- result |>
  select(-any_of(c("loglik.se", "sample", "flag", "loglik"))) |>
  mutate(id = seq(1, nrow(result), 1)) |> # To create a unique column required to make that data in long form
  pivot_longer(-id) |> # To make the data in long form required for `tidyverse`
  group_by(name) |> # Based on which column you want aggregate
  identify_outliers(value) |>
  select(id, is.outlier) |>
  distinct_all() |>
  arrange(desc(id))

result |>
  mutate(id = seq(1, nrow(result), 1)) |>
  left_join(outlier_list) |>
  replace_na(list(is.outlier = FALSE)) |>
  # filter(!is.outlier) |>
  select(-any_of(c("loglik.se", "sample", "flag"))) |>
  pivot_longer(-c(loglik, is.outlier)) |>
  ggplot(aes(x = value, y = loglik, color = is.outlier)) +
  facet_wrap(~name, scales = "free_x") +
  geom_point() +
  theme_bw(8)

# output_dir <- "param_grids/Ahmedabad/hadISD/"
# if (!dir.exists(output_dir)) {
#   dir.create(output_dir, recursive = TRUE)
# }
# output_file_path <- file.path(output_dir, "my_data.csv")

generate_grid(result, diff_LL = 20, output_dir = "param_grids/Surat/baseline")
```

## Testing fitting
