---
title: "Parameter profiles"
author: "Leonardo Souto Ferreira"
date: today
format: html
toc: TRUE
execute:
  message: FALSE
  warning: FALSE
  echo: FALSE
  eval: TRUE
knitr:
  opts_knit:
    root.dir: "/home/leonardo/Doutorado/RH_update_paper/"
geometry:
  - margin=2cm
---

```{r, message = F, eval = TRUE}
library(tidyverse)
source("R/mcap.R")
source("R/cleaning_profile_results.R")

param_groups <- list(
  transmission = c("b1", "b2", "b3", "b4", "b5", "b6", "bH", "betaOUT", "alpha"),
  initial = c("S1_0", "S2_0", "E_0", "I1_0", "I2_0", "F_0", "K_0"),
  immunity = c("muEI1", "muS2S1", "muI1S2", "muI2S2", "q0", "rho", "tau", "sigOBS", "sigPRO")
)
```

# Parameter transforms

All four profile files were produced with the `inf_exponent` model, so the
estimation-scale transform is the one defined in
`dynamical_model/fitting/pomp_object_inf_exponent.R` (fed to pomp via
`parameter_trans(log=, logit=, barycentric=)` in `prepare_pomp_model()`).
MCAP's loess/quadratic machinery assumes an approximately quadratic
log-likelihood surface, which only holds on the scale the model was actually
fit on — so profile CIs need to be computed after transforming to that scale,
then mapped back to the natural scale for plotting.

```{r, eval = TRUE}
model_env <- new.env()
sys.source("dynamical_model/fitting/pomp_object_inf_exponent.R", envir = model_env)

# S1_0/E_0/I1_0/S2_0/I2_0 are barycentric-transformed as a group:
# T_i = log(theta_i / sum(theta)). But pomp's fromEst always reconstructs the
# natural-scale values with sum(theta) == 1 (verified on every row of all 4
# profile files), so T_i = log(theta_i) exactly here -- a plain log transform.
log_scale_params <- c(model_env$log_transf, model_env$barycentric_transf)
logit_scale_params <- model_env$logit_transf

#' Vectorized over `name` (so it also works on a multi-parameter data frame,
#' not just a single already-split-out parameter).
param_scale <- function(name) {
  case_when(
    name %in% log_scale_params ~ "log",
    name %in% logit_scale_params ~ "logit",
    TRUE ~ "identity"
  )
}

#' Vectorized over `scale` too (a single scale string is recycled as usual).
#' case_when() evaluates every branch's RHS across the whole vector before
#' picking per-element which one applies, so e.g. qlogis() on a log-scale
#' parameter's (out-of-[0,1]-range) value harmlessly warns "NaNs produced"
#' even though that NaN is never selected; suppressWarnings() here is only
#' silencing that non-issue, not hiding a real one.
to_est <- function(value, scale) {
  suppressWarnings(case_when(
    scale == "log" ~ log(value),
    scale == "logit" ~ qlogis(value),
    TRUE ~ value
  ))
}

from_est <- function(value, scale) {
  suppressWarnings(case_when(
    scale == "log" ~ exp(value),
    scale == "logit" ~ plogis(value),
    TRUE ~ value
  ))
}
```

# Plot conventions

Black points are Monte Carlo estimates of the profile log-likelihood from the
retained parameter fits; the blue curve is the loess-smoothed profile used
for MCAP inference. The vermillion solid vertical line marks the true
(unrestricted) MLE -- the single best raw log-likelihood evaluation across
the whole retained dataset, i.e. the same fitted parameter vector for every
panel -- and the orange dashed vertical lines mark the 95% MCAP confidence
limits. The bottom-center annotation in each panel gives
`MLE [CI low, CI high] (Δ=delta)` to ~3 significant digits; a confidence
limit that rounds to the parameter's natural boundary (e.g. `[..., 1.00]`
for a logit-scale parameter) indicates the profile is boundary-limited
rather than showing a conventional interior optimum. `delta` is the
log-likelihood drop `mcap_checked()` used to define the CI cutoff (the
profile is "inside" the CI wherever the smoothed curve is within `delta` of
its own maximum) -- i.e. how much loglik had to be given up to bound the
parameter; `delta` is `NA` when the quadratic fit isn't concave, in which
case the reported CI is just the explored parameter range, not a real MCAP
interval (both bounds will also show as truncated). Unless noted otherwise, the y-axis shows log-likelihood *relative
to* that same true MLE (not the loess-smoothed maximum, which is noisier and
per-panel), with a shared range computed from the plotted data so panels
stay comparable; a curve poking above 0 flags Monte Carlo noise in the
profile (see recommendation #14 in the source recommendations) rather than a
better fit than the MLE. x-axes remain free per panel since parameter
domains differ (unconstrained coefficients, positive rates, probabilities,
proportions). Parameters were fit, and MCAP confidence intervals computed,
on their estimation scale (see "Parameter transforms" above); this figure
shows them back-transformed to the natural/biological scale, with a
transformed-scale diagnostic version available via
`plot_profile_group_transformed()` to check the underlying fit quality.

```{r, eval = TRUE}
#' Format to ~`digits` significant figures: fixed notation in a normal range,
#' scientific notation for very small/large magnitudes. Used instead of a
#' fixed number of decimal places so labels stay compact whether the
#' parameter is ~1e-8 or ~600.
fmt_sig <- function(x, digits = 3) {
  vapply(x, function(xi) {
    if (is.na(xi)) {
      return(NA_character_)
    }
    if (xi != 0 && (abs(xi) < 1e-3 || abs(xi) >= 1e3)) {
      formatC(xi, format = "e", digits = digits - 1)
    } else {
      sub("\\.$", "", formatC(signif(xi, digits), format = "fg", digits = digits, flag = "#"))
    }
  }, character(1))
}

#' "mle [ci_1, ci_2] (delta=...)", ~3 significant figures -- the compact
#' annotation used in every profile panel instead of repeating "MLE:"/"CI:"
#' labels. A bound flagged `*_truncated` (mcap_checked(): non-concave fit,
#' edge maximum, or too few local points -- see R/mcap.R) is not an actual
#' MCAP threshold crossing, just the edge of the explored profile range, so
#' it's shown as "<value"/">value" (true bound unknown beyond that point)
#' rather than as if it were a properly estimated limit. `delta` is the
#' log-likelihood drop mcap_checked() used to define the CI (the profile is
#' "inside" the CI wherever smoothed loglik is within `delta` of its own
#' max) -- how much of the loglik had to be given up to bound the parameter;
#' NA (non-concave fit -- no valid delta) is shown as literal "NA" via
#' fmt_sig()/paste0()'s normal NA-to-text handling, not a special case here.
fmt_mle_ci <- function(mle, ci_1, ci_2, ci_1_truncated = FALSE, ci_2_truncated = FALSE,
                       delta = NA_real_, digits = 3) {
  lo <- paste0(ifelse(ci_1_truncated, "<", ""), fmt_sig(ci_1, digits))
  hi <- paste0(ifelse(ci_2_truncated, ">", ""), fmt_sig(ci_2, digits))
  paste0(fmt_sig(mle, digits), " [", lo, ", ", hi, "] (Δ=", fmt_sig(delta, digits), ")")
}

# Publication-quality facet labels (plotmath) for the natural-scale plot.
parameter_labels <- c(
  alpha = "alpha",
  b1 = "b[1]", b2 = "b[2]", b3 = "b[3]", b4 = "b[4]", b5 = "b[5]", b6 = "b[6]",
  bH = "b[H]",
  betaOUT = "beta[out]",
  muEI1 = "mu[EI1]",
  muS2S1 = "mu[S2*S1]",
  muI1S2 = "mu[I1*S2]",
  muI2S2 = "mu[I2*S2]",
  q0 = "q[0]",
  rho = "rho",
  tau = "tau",
  sigOBS = "sigma[obs]",
  sigPRO = "sigma[proc]",
  S1_0 = "S[1]^0",
  S2_0 = "S[2]^0",
  E_0 = "E^0",
  I1_0 = "I[1]^0",
  I2_0 = "I[2]^0",
  K_0 = "K^0",
  F_0 = "F^0"
)

# Okabe-Ito colorblind-safe palette, matching the manuscript figures in
# new_figures.qmd. Curve = blue, MLE line = vermillion, CI lines = orange.
okabe_ito <- c(
  orange = "#E69F00", skyblue = "#56B4E9", green = "#009E73", yellow = "#F0E442",
  blue = "#0072B2", vermillion = "#D55E00", purple = "#CC79A7", black = "#000000"
)

#' Shared look for the profile-likelihood plots, matching the manuscript
#' figures in new_figures.qmd (minimal theme, black axis lines, no minor
#' gridlines, Helvetica).
theme_profile <- function(base_size) {
  theme_minimal(base_size = base_size, base_family = "sans") +
    theme(
      axis.line = element_line(color = "black"),
      legend.position = "none",
      panel.grid.minor = element_blank(),
      text = element_text(family = "Helvetica")
    )
}
```

# Helper functions

```{r, eval = TRUE}
#' Reduce a parameter's (value, loglik) pairs to one row per DISTINCT focal
#' value: the single best (max) log-likelihood evaluation at that value. This
#' is what a profile-likelihood run actually is -- the focal parameter is
#' fixed at a grid of values and every other parameter is re-optimized at
#' each one -- so grouping by the focal parameter's own exact value and
#' taking the best of however many replicate optimizations landed there
#' recovers the profile directly; no binning needed, and no z-score/IQR
#' trimming either (a value being unusual among the sampled cloud says
#' nothing about whether its likelihood is relevant, and profile tails,
#' where CI endpoints live, are exactly where trimming would cut).
#'
#' When the data carries a `profile_var` column (recording which parameter
#' was actually held fixed for a given row -- currently only
#' profile_Ahmedabad_hadISD_1997_2011_8_9.csv), rows are first restricted to
#' `profile_var == name`: this parameter's own profile run, not the whole
#' multi-parameter file. Without `profile_var`, the same
#' group-by-exact-value logic runs on the whole dataset instead (rows from
#' OTHER parameters' profile runs, where this one was itself free to vary,
#' essentially never land on exactly the same value twice, so they just
#' contribute as their own single-row group -- a reasonable but noisier
#' approximation of the same thing).
#'
#' `diff_LL` is applied relative to THIS parameter's own best loglik within
#' its (possibly profile_var-isolated) subset, not some unrelated global
#' optimum, and widens automatically if too few distinct grid values survive
#' it for a stable MCAP quadratic fit. `n_replicates` (kept as diagnostic
#' metadata) is how many rows shared that exact value before picking the
#' best one.
focal_profile_points <- function(dataset, diff_LL = 10, min_points = 20) {
  dataset <- dataset[complete.cases(dataset), ] |>
    filter(loglik >= max(loglik) - diff_LL)

  focal_name <- unique(dataset$name)
  if ("profile_var" %in% names(dataset)) {
    dataset <- dataset |> filter(profile_var == focal_name)
  }

  if (nrow(dataset) == 0) {
    return(dataset |> mutate(n_replicates = integer(0)))
  }
  reduced <- dataset |>
    group_by(value) |>
    mutate(n_replicates = n()) |>
    slice_max(loglik, n = 1, with_ties = FALSE) |>
    ungroup()

  return(reduced)
}

plot_mcap_binned_2 <- function(dataset, diff_LL = 10, min_points = 20) {
  scale <- param_scale(unique(dataset$name))
  dataset <- focal_profile_points(dataset, diff_LL = diff_LL, min_points = min_points)

  if (nrow(dataset) < 4) {
    return(tibble(
      parameter = NA_real_, smoothed = NA_real_, quadratic = NA_real_,
      ci_1 = NA_real_, ci_2 = NA_real_,
      ci_1_truncated = NA, ci_2_truncated = NA, delta = NA_real_
    ))
  }

  parameter <- to_est(dataset$value, scale)
  lp <- dataset$loglik
  mcap_res <- mcap_checked(lp, parameter, lambda = 0.75)

  with(mcap_res, {
    if (is.infinite(ci[1])) ci[1] <- min(parameter)
    if (is.infinite(ci[2])) ci[2] <- max(parameter)

    fit |>
      mutate(
        parameter = from_est(parameter, scale),
        ci_1 = from_est(ci[1], scale),
        ci_2 = from_est(ci[2], scale),
        ci_1_truncated = ci_truncated[["lower"]],
        ci_2_truncated = ci_truncated[["upper"]],
        delta = delta
      ) |>
      as_tibble()
  })
}

#' Read one profile-likelihood CSV, keep the acceptable region (mirroring the
#' "mode" bookkeeping column present in some refined profile files but not
#' others), and compute the MCAP-smoothed curve, its CI, and the per-value
#' best-likelihood points (focal_profile_points()) for every parameter.
analyze_profile <- function(profile_file, city, covariate_label, output_prefix) {
  all_res <- read_csv(profile_file, show_col_types = FALSE)
  all_res <- all_res |>
    select(-any_of(c("flag", "loglik.se", "sample", "mode", "source_file"))) |>
    filter(rho >= 0.01)
  all_res <- all_res |> filter(alpha > 0, alpha <= 1)

  smoothed_curves <- all_res |>
    select(-delta) |>
    pivot_longer(-any_of(c("loglik", "profile_var"))) |>
    split(~name) |>
    lapply(plot_mcap_binned_2, diff_LL = 20) |>
    bind_rows(.id = "name") |>
    rename(value = parameter)

  ci_vals <- smoothed_curves |>
    select(name, ci_1, ci_2) |>
    distinct() |>
    pivot_longer(-name, names_to = "name2") |>
    rename(ci = value) |>
    select(-name2)

  mle_vals <- all_res |>
    select(-delta) |>
    pivot_longer(-any_of(c("loglik", "profile_var"))) |>
    group_by(name) |>
    slice_max(loglik) |>
    ungroup() |>
    select(name, value) |>
    rename(mle = value)

  smoothed_curves <- smoothed_curves |>
    left_join(mle_vals, by = "name") |>
    mutate(label = fmt_mle_ci(mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, delta))

  smoothed_curves |>
    select(name, mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, delta) |>
    distinct() |>
    mutate(
      label = fmt_mle_ci(mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, delta),
      city = city, covariate = covariate_label
    ) |>
    select(city, covariate, name, label) |>
    write_csv(str_glue("figures/{output_prefix}_parameters_profile.csv"))

  # Same reduction (and same possibly-widened likelihood window) as
  # plot_mcap_binned_2() above, so the plotted points match what the MCAP
  # curve was actually fit to; see focal_profile_points() and "Plot
  # conventions" above.
  binned <- all_res |>
    select(-delta) |>
    pivot_longer(-any_of(c("loglik", "profile_var"))) |>
    split(~name) |>
    lapply(focal_profile_points, diff_LL = 20) |>
    bind_rows(.id = "name")

  # Reference for relative log-likelihood: the true (unrestricted) MLE's own
  # raw log-likelihood -- the same single best-fit row used for mle_vals
  # above, not the (per-panel, noisier) loess-smoothed curve maximum.
  mle_loglik <- max(all_res$loglik)

  list(
    binned = binned, smoothed_curves = smoothed_curves, ci_vals = ci_vals,
    mle_vals = mle_vals, mle_loglik = mle_loglik
  )
}

#' Subtract the true MLE's log-likelihood (a single scalar, shared by every
#' panel -- see analyze_profile()) from `loglik`/`smoothed`, for
#' relative-log-likelihood plotting (see "Plot conventions").
apply_relative_loglik <- function(binned, smoothed_curves, mle_loglik) {
  list(
    binned = binned |> mutate(loglik = loglik - mle_loglik),
    smoothed_curves = smoothed_curves |> mutate(smoothed = smoothed - mle_loglik)
  )
}

#' Compute a shared y-limit from the actual (post-relative) data being
#' plotted, rather than a guessed fixed window -- a real "global y-axis"
#' that adapts to whatever names_subset/profile is passed in, with a little
#' padding and always including 0 (the MLE's own level).
relative_ylim <- function(binned, smoothed_curves, pad = 0.5) {
  vals <- c(binned$loglik, smoothed_curves$smoothed, 0)
  vals <- vals[is.finite(vals)]
  range(vals) + c(-pad, pad)
}

#' Profile-likelihood plot: points (raw MC loglik evaluations) + MCAP-smoothed
#' curve + solid MLE line + dashed CI lines + a compact "mle [ci_1, ci_2]"
#' annotation in each panel's top-left corner. One facet per parameter;
#' `names_subset = NULL` plots every parameter in one grid. `relative = TRUE`
#' (default) plots log-likelihood relative to the true MLE (see
#' analyze_profile()), with a shared y-axis across panels (`ylim = NULL`
#' computes it from the plotted data via relative_ylim(); pass an explicit
#' `c(low, high)` to fix it, e.g. for comparing multiple saved figures) so
#' identifiability is comparable across parameters; x stays free per panel.
plot_profile_group <- function(profile, names_subset = NULL, base_size = 22, label_size = 5,
                               relative = TRUE, ylim = NULL) {
  binned <- profile$binned
  smoothed_curves <- profile$smoothed_curves
  ci_vals <- profile$ci_vals
  mle_vals <- profile$mle_vals

  if (!is.null(names_subset)) {
    binned <- binned |> filter(name %in% names_subset)
    smoothed_curves <- smoothed_curves |> filter(name %in% names_subset)
    ci_vals <- ci_vals |> filter(name %in% names_subset)
    mle_vals <- mle_vals |> filter(name %in% names_subset)
  }

  y_lab <- "Log-likelihood"
  if (relative) {
    rel <- apply_relative_loglik(binned, smoothed_curves, profile$mle_loglik)
    binned <- rel$binned
    smoothed_curves <- rel$smoothed_curves
    y_lab <- "Relative log-likelihood"
    if (is.null(ylim)) ylim <- relative_ylim(binned, smoothed_curves)
  }

  # The global MLE's own point (see analyze_profile()) usually isn't part of
  # THIS parameter's own profile_var subset, so it's not among `binned`'s
  # points -- draw it explicitly rather than relying on it to show up by
  # coincidence, so the vline always has a visible point to go with it.
  mle_vals <- mle_vals |> mutate(mle_y = if (relative) 0 else profile$mle_loglik)

  # Bottom-center anchor per panel: mean of the smoothed curve's own x-range
  # approximates each free-x panel's horizontal midpoint.
  labels <- smoothed_curves |>
    group_by(name) |>
    summarize(label = first(label), xpos = mean(range(value)), .groups = "drop")

  p <- binned |>
    left_join(smoothed_curves |> select(name, ci_1, ci_2, delta) |> distinct(), by = "name") |>
    ggplot(aes(x = value, y = loglik)) +
    facet_wrap(~name,
      scales = if (relative) "free_x" else "free",
      labeller = labeller(name = as_labeller(parameter_labels, label_parsed))
    ) +
    geom_point(size = 0.6, alpha = 0.4) +
    geom_line(aes(y = smoothed), data = smoothed_curves, color = okabe_ito[["blue"]], linewidth = 0.7) +
    geom_vline(aes(xintercept = mle), data = mle_vals, color = okabe_ito[["vermillion"]], linewidth = 0.5, linetype = "solid") +
    geom_point(aes(x = mle, y = mle_y), data = mle_vals, inherit.aes = FALSE, color = okabe_ito[["vermillion"]], size = 1.3) +
    geom_vline(aes(xintercept = ci), data = ci_vals, color = okabe_ito[["orange"]], linewidth = 0.5, linetype = "dashed") +
    geom_label(aes(x = xpos, y = -Inf, label = label),
      data = labels, inherit.aes = FALSE,
      hjust = 0.5, vjust = -0.3, size = label_size,
      fill = "white", alpha = 0.7, linewidth = 0,
      label.padding = unit(0.12, "lines")
    ) +
    theme_profile(base_size) +
    labs(x = "Parameter value", y = y_lab)

  if (relative) {
    p <- p + coord_cartesian(ylim = ylim)
  }
  p
}

#' Same diagnostic as plot_profile_group(), but on each parameter's
#' *estimation* scale (log/logit/identity; see param_scale()) instead of its
#' natural scale. MCAP's loess/quadratic fit assumes it's fitting an
#' approximately quadratic surface on THIS scale, so a misbehaved
#' estimation -- a bad loess fit, a boundary artifact, a non-monotonic wiggle
#' -- is best diagnosed here; the natural-scale plot can look fine even when
#' the underlying fit is not, since back-transforming can visually smooth
#' over problems. The MLE/CI annotation stays in natural-scale units (same
#' label as the natural-scale plot) so the two are easy to cross-reference.
plot_profile_group_transformed <- function(profile, names_subset = NULL, base_size = 22, label_size = 5,
                                           relative = TRUE, ylim = NULL) {
  binned <- profile$binned
  smoothed_curves <- profile$smoothed_curves
  ci_vals <- profile$ci_vals
  mle_vals <- profile$mle_vals

  if (!is.null(names_subset)) {
    binned <- binned |> filter(name %in% names_subset)
    smoothed_curves <- smoothed_curves |> filter(name %in% names_subset)
    ci_vals <- ci_vals |> filter(name %in% names_subset)
    mle_vals <- mle_vals |> filter(name %in% names_subset)
  }

  y_lab <- "Log-likelihood"
  if (relative) {
    rel <- apply_relative_loglik(binned, smoothed_curves, profile$mle_loglik)
    binned <- rel$binned
    smoothed_curves <- rel$smoothed_curves
    y_lab <- "Relative log-likelihood"
    if (is.null(ylim)) ylim <- relative_ylim(binned, smoothed_curves)
  }

  binned <- binned |> mutate(value = to_est(value, param_scale(name)))
  smoothed_curves <- smoothed_curves |>
    mutate(
      value = to_est(value, param_scale(name)),
      ci_1 = to_est(ci_1, param_scale(name)),
      ci_2 = to_est(ci_2, param_scale(name))
    )
  ci_vals <- ci_vals |> mutate(ci = to_est(ci, param_scale(name)))
  mle_vals <- mle_vals |>
    mutate(
      mle = to_est(mle, param_scale(name)),
      mle_y = if (relative) 0 else profile$mle_loglik
    )

  # Bottom-center anchor per panel: mean of the smoothed curve's own x-range
  # approximates each free-x panel's horizontal midpoint.
  labels <- smoothed_curves |>
    group_by(name) |>
    summarize(label = first(label), xpos = mean(range(value)), .groups = "drop")
  facet_labels <- setNames(
    paste0(unique(binned$name), " (", param_scale(unique(binned$name)), ")"),
    unique(binned$name)
  )

  p <- binned |>
    left_join(smoothed_curves |> select(name, ci_1, ci_2, delta) |> distinct(), by = "name") |>
    ggplot(aes(x = value, y = loglik)) +
    facet_wrap(~name,
      scales = if (relative) "free_x" else "free",
      labeller = labeller(name = facet_labels)
    ) +
    geom_point(size = 0.6, alpha = 0.4) +
    geom_line(aes(y = smoothed), data = smoothed_curves, color = okabe_ito[["blue"]], linewidth = 0.7) +
    geom_vline(aes(xintercept = mle), data = mle_vals, color = okabe_ito[["vermillion"]], linewidth = 0.5, linetype = "solid") +
    geom_vline(aes(xintercept = ci), data = ci_vals, color = okabe_ito[["orange"]], linewidth = 0.5, linetype = "dashed") +
    geom_label(aes(x = xpos, y = -Inf, label = label),
      data = labels, inherit.aes = FALSE,
      hjust = 0.5, vjust = -0.3, size = label_size,
      fill = "white", alpha = 0.7, linewidth = 0,
      label.padding = unit(0.12, "lines")
    ) +
    theme_profile(base_size) +
    labs(x = "Parameter value (estimation scale)", y = y_lab)

  if (relative) {
    p <- p + coord_cartesian(ylim = ylim)
  }
  p
}

#' Draw a parameter-group plot, print it (so it renders in the document), and
#' save it to `filename`.
save_profile_plot <- function(profile, names_subset, filename, label_size = 5, base_size = 22,
                              width = 14, height = 14, dpi = 600) {
  p <- plot_profile_group(profile, names_subset, base_size = base_size, label_size = label_size)
  print(p)
  ggsave(filename, plot = p, width = width, height = height, dpi = dpi)
  invisible(p)
}
```

# Ahmedabad, relative humidity

```{r, fig.height = 20, fig.width = 20, eval = TRUE}
ahmedabad_rh <- analyze_profile(
  "aggregated_results/all_profiles.csv",
  city = "Ahmedabad", covariate_label = "Relative humidity", output_prefix = "Ahmedabad_RH"
)

print(plot_profile_group(ahmedabad_rh, base_size = 12, label_size = 5))
print(plot_profile_group_transformed(ahmedabad_rh, base_size = 12, label_size = 5))

save_profile_plot(ahmedabad_rh, param_groups$transmission, "figures/profile_Ahmedabad_RH_transmission.pdf")
save_profile_plot(ahmedabad_rh, param_groups$initial, "figures/profile_Ahmedabad_RH_initial.pdf")
save_profile_plot(ahmedabad_rh, param_groups$immunity, "figures/profile_Ahmedabad_RH_immunity.pdf")
```

# Ahmedabad, maximum temperature

```{r, fig.height = 20, fig.width = 20, eval = FALSE}
ahmedabad_temp <- analyze_profile(
  "aggregated_results/profile_Ahmedabad_Max_Temp_1997_2011_9_9.csv",
  city = "Ahmedabad", covariate_label = "Maximum temperature", output_prefix = "Ahmedabad_Max_Temp"
)
print(plot_profile_group(ahmedabad_temp, base_size = 12, label_size = 5))

print(plot_profile_group_transformed(ahmedabad_temp, base_size = 12, label_size = 5))

save_profile_plot(ahmedabad_temp, param_groups$transmission, "figures/profile_Ahmedabad_Max_Temp_transmission.pdf")
save_profile_plot(ahmedabad_temp, param_groups$initial, "figures/profile_Ahmedabad_Max_Temp_initial.pdf")
save_profile_plot(ahmedabad_temp, param_groups$immunity, "figures/profile_Ahmedabad_Max_Temp_immunity.pdf")
```

# Surat, relative humidity

```{r, fig.height = 20, fig.width = 20, eval = FALSE}
surat_rh <- analyze_profile(
  "aggregated_results/profile_Surat_hadISD_1997_2016_7_7.csv",
  city = "Surat", covariate_label = "Relative humidity", output_prefix = "Surat_RH"
)
print(plot_profile_group(surat_rh, base_size = 12, label_size = 5))

print(plot_profile_group_transformed(surat_rh, base_size = 12, label_size = 5))

save_profile_plot(surat_rh, param_groups$transmission, "figures/profile_Surat_RH_transmission.pdf")
save_profile_plot(surat_rh, param_groups$initial, "figures/profile_Surat_RH_initial.pdf")
save_profile_plot(surat_rh, param_groups$immunity, "figures/profile_Surat_RH_immunity.pdf")
```

# Surat, maximum temperature

```{r, fig.height = 20, fig.width = 20, eval = FALSE}
surat_temp <- analyze_profile(
  "aggregated_results/profile_Surat_Max_Temp_1997_2016_5_9.csv",
  city = "Surat", covariate_label = "Maximum temperature", output_prefix = "Surat_Max_Temp"
)
print(plot_profile_group(surat_temp, base_size = 12, label_size = 5))

print(plot_profile_group_transformed(surat_temp, base_size = 12, label_size = 5))

save_profile_plot(surat_temp, param_groups$transmission, "figures/profile_Surat_Max_Temp_transmission.pdf")
save_profile_plot(surat_temp, param_groups$initial, "figures/profile_Surat_Max_Temp_initial.pdf")
save_profile_plot(surat_temp, param_groups$immunity, "figures/profile_Surat_Max_Temp_immunity.pdf")
```
