---
title: "Parameter profiles"
author: "Leonardo Souto Ferreira"
date: today
format: html
toc: TRUE
execute:
  message: FALSE
  warning: FALSE
  echo: FALSE
  eval: TRUE
geometry:
  - margin=2cm
---

```{r, message = F, eval = TRUE}
proj_root <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
setwd(proj_root)
knitr::opts_knit$set(root.dir = proj_root)
pkgload::load_all(proj_root)
library(tidyverse)

param_groups <- list(
  transmission = c("b1", "b2", "b3", "b4", "b5", "b6", "bH", "betaOUT", "alpha"),
  initial = c("S1_0", "S2_0", "E_0", "I1_0", "I2_0", "F_0", "K_0"),
  immunity = c("muEI1", "muS2S1", "muI1S2", "muI2S2", "q0", "rho", "tau", "sigOBS", "sigPRO")
)
# Mechanistic grouping (transmission / initial conditions / immunity) used
# to order both the CSV tables and the plot facets.
param_order <- unlist(param_groups, use.names = FALSE)
```

# Parameter transforms

All four profile files were produced with the `inf_exponent` model, so the
estimation-scale transform is the one defined in
`dynamical_model/fitting/pomp_object_inf_exponent.R` (fed to pomp via
`parameter_trans(log=, logit=, barycentric=)` in `prepare_pomp_model()`).
MCAP's loess/quadratic machinery assumes an approximately quadratic
log-likelihood surface, which only holds on the scale the model was actually
fit on — so profile CIs need to be computed after transforming to that scale,
then mapped back to the natural scale for plotting.

```{r, eval = TRUE}
model_env <- new.env()
sys.source("dynamical_model/fitting/pomp_object_inf_exponent.R", envir = model_env)
log_scale_params <- c(model_env$log_transf, model_env$barycentric_transf)
logit_scale_params <- model_env$logit_transf
param_scale <- function(name) {
  case_when(
    name %in% log_scale_params ~ "log",
    name %in% logit_scale_params ~ "logit",
    TRUE ~ "identity"
  )
}
to_est <- function(value, scale) {
  suppressWarnings(case_when(
    scale == "log" ~ log(value),
    scale == "logit" ~ qlogis(value),
    TRUE ~ value
  ))
}

from_est <- function(value, scale) {
  suppressWarnings(case_when(
    scale == "log" ~ exp(value),
    scale == "logit" ~ plogis(value),
    TRUE ~ value
  ))
}
```

# Plot conventions

Points are Monte Carlo log-likelihood evaluations; the blue curve is the
MCAP-smoothed profile. The vermillion line/point mark the true MLE (the
single best fit across the whole file, the same for every panel); the
orange dashed lines mark the 95% MCAP confidence limits. Each panel's label
reads `MLE [CI low, CI high] (Δ=delta)`: a `<`/`>` prefix on a bound means
it's just the edge of the explored range, not a real MCAP crossing (fit
wasn't concave, or too few points), and `delta` is the log-likelihood drop
used to define the CI (`NA` when non-concave). The y-axis is log-likelihood
relative to the true MLE, shared across panels; x-axes stay free per panel.
Parameters are fit and profiled on their estimation scale (see "Parameter
transforms" above) and shown here back-transformed;
`plot_profile_group_transformed()` shows the estimation-scale version.


```{r, eval = TRUE}
fmt_sig <- function(x, digits = 3) {
  vapply(x, function(xi) {
    if (is.na(xi)) {
      return(NA_character_)
    }
    if (xi != 0 && (abs(xi) < 1e-3 || abs(xi) >= 1e3)) {
      formatC(xi, format = "e", digits = digits - 1)
    } else {
      sub("\\.$", "", formatC(signif(xi, digits), format = "fg", digits = digits, flag = "#"))
    }
  }, character(1))
}
fmt_mle_ci <- function(mle, ci_1, ci_2, ci_1_truncated = FALSE, ci_2_truncated = FALSE,
                       delta = NA_real_, digits = 3, delta_symbol = "Δ", include_delta = TRUE,
                       delta_sep = " ") {
  lo <- paste0(ifelse(ci_1_truncated, "<", ""), fmt_sig(ci_1, digits))
  hi <- paste0(ifelse(ci_2_truncated, ">", ""), fmt_sig(ci_2, digits))
  label <- paste0(fmt_sig(mle, digits), " [", lo, ", ", hi, "]")
  if (include_delta) {
    label <- paste0(label, delta_sep, "(", delta_symbol, "=", fmt_sig(delta, digits), ")")
  }
  label
}

# Publication-quality facet labels (plotmath) for the natural-scale plot.
parameter_labels <- c(
  alpha = "alpha",
  b1 = "b[1]", b2 = "b[2]", b3 = "b[3]", b4 = "b[4]", b5 = "b[5]", b6 = "b[6]",
  bH = "b[H]",
  betaOUT = "beta[out]",
  muEI1 = "mu[EI1]",
  muS2S1 = "mu[S2*S1]",
  muI1S2 = "mu[I1*S2]",
  muI2S2 = "mu[I2*S2]",
  q0 = "q[0]",
  rho = "rho",
  tau = "tau",
  sigOBS = "sigma[obs]",
  sigPRO = "sigma[proc]",
  S1_0 = "S[1]^0",
  S2_0 = "S[2]^0",
  E_0 = "E^0",
  I1_0 = "I[1]^0",
  I2_0 = "I[2]^0",
  K_0 = "K^0",
  F_0 = "F^0"
)

# Same parameter labels, as LaTeX math (for the CSV output, which feeds
# LaTeX tables rather than ggplot facets).
parameter_labels_latex <- c(
  alpha = "$\\alpha$",
  b1 = "$b_1$", b2 = "$b_2$", b3 = "$b_3$", b4 = "$b_4$", b5 = "$b_5$", b6 = "$b_6$",
  bH = "$b_H$",
  betaOUT = "$\\beta_{out}$",
  muEI1 = "$\\mu_{EI1}$",
  muS2S1 = "$\\mu_{S2S1}$",
  muI1S2 = "$\\mu_{I1S2}$",
  muI2S2 = "$\\mu_{I2S2}$",
  q0 = "$q_0$",
  rho = "$\\rho$",
  tau = "$\\tau$",
  sigOBS = "$\\sigma_{obs}$",
  sigPRO = "$\\sigma_{proc}$",
  S1_0 = "$S_1^0$",
  S2_0 = "$S_2^0$",
  E_0 = "$E^0$",
  I1_0 = "$I_1^0$",
  I2_0 = "$I_2^0$",
  K_0 = "$K^0$",
  F_0 = "$F^0$"
)

# Okabe-Ito colorblind-safe palette, matching the manuscript figures in
# new_figures.qmd. Curve = blue, MLE line = vermillion, CI lines = orange.
okabe_ito <- c(
  orange = "#E69F00", skyblue = "#56B4E9", green = "#009E73", yellow = "#F0E442",
  blue = "#0072B2", vermillion = "#D55E00", purple = "#CC79A7", black = "#000000"
)

#' Shared look for the profile-likelihood plots, matching the manuscript
#' figures in new_figures.qmd (minimal theme, black axis lines, no minor
#' gridlines, Helvetica).
theme_profile <- function(base_size) {
  theme_minimal(base_size = base_size, base_family = "sans") +
    theme(
      axis.line = element_line(color = "black"),
      legend.position = "none",
      panel.grid.minor = element_blank(),
      text = element_text(family = "Helvetica")
    )
}
```

# Helper functions

```{r, eval = TRUE}
#' Equal-width bins over x's own range (unlike quantile bins, which
#' over-sample flat tails and under-sample a sharp peak).
bin_uniform <- function(x, n_bins = 40) {
  rng <- range(x, na.rm = TRUE)
  width <- diff(rng)
  if (!is.finite(width) || width == 0) {
    return(list(bin = rep(1L, length(x)), bin_start = rep(rng[1], length(x)), bin_end = rep(rng[1], length(x))))
  }
  breaks <- seq(rng[1], rng[2], length.out = n_bins + 1)
  bin <- pmin(pmax(findInterval(x, breaks, rightmost.closed = TRUE), 1L), n_bins)
  list(bin = bin, bin_start = breaks[bin], bin_end = breaks[bin + 1])
}

focal_profile_points <- function(dataset, diff_LL = 10, min_points = 30, max_diff_LL = 50, n_bins = 40) {
  dataset <- dataset[complete.cases(dataset), ]
  scale <- param_scale(unique(dataset$name))
  dataset <- dataset |> mutate(est_value = to_est(value, scale))

  repeat {
    windowed <- if (is.null(diff_LL)) {
      dataset
    } else {
      dataset |> filter(loglik >= max(loglik) - diff_LL)
    }

    bins <- bin_uniform(windowed$est_value, n_bins = n_bins)
    reduced <- windowed |>
      mutate(bin = bins$bin, bin_start = bins$bin_start, bin_end = bins$bin_end) |>
      group_by(bin) |>
      slice_max(loglik, n = 1, with_ties = FALSE) |>
      ungroup()

    enough <- nrow(reduced) >= min_points
    if (is.null(diff_LL) || enough || diff_LL >= max_diff_LL) {
      return(reduced)
    }
    diff_LL <- diff_LL * 2
  }
}

#' Fit mcap_checked() on focal_profile_points()'s reduced points (passed in
#' directly, so the curve is always fit on exactly what's plotted) and
#' transform the curve/CI back to the natural scale. Returns an NA
#' placeholder instead of erroring when there's too little data to fit.
plot_mcap_binned_2 <- function(dataset, lambda = 0.4) {
  scale <- param_scale(unique(dataset$name))

  if (nrow(dataset) < 4) {
    return(tibble(
      parameter = NA_real_, smoothed = NA_real_, quadratic = NA_real_,
      ci_1 = NA_real_, ci_2 = NA_real_,
      ci_1_truncated = NA, ci_2_truncated = NA, delta = NA_real_
    ))
  }

  parameter <- dataset$est_value
  lp <- dataset$loglik
  mcap_res <- mcap_checked(lp, parameter, lambda = lambda)

  with(mcap_res, {
    if (is.infinite(ci[1])) ci[1] <- min(parameter)
    if (is.infinite(ci[2])) ci[2] <- max(parameter)

    fit |>
      mutate(
        parameter = from_est(parameter, scale),
        ci_1 = from_est(ci[1], scale),
        ci_2 = from_est(ci[2], scale),
        ci_1_truncated = ci_truncated[["lower"]],
        ci_2_truncated = ci_truncated[["upper"]],
        delta = delta
      ) |>
      as_tibble()
  })
}

analyze_profile <- function(profile_file, output_prefix,
                            diff_LL = 10, min_points = 60, max_diff_LL = 50,
                            n_bins = 30, lambda = 0.6, digits = 3) {
  all_res <- read_csv(profile_file, show_col_types = FALSE)
  all_res <- all_res |>
    select(-any_of(c("flag", "loglik.se", "sample", "mode", "source_file", "profile_var"))) |>
    filter(rho >= 0.01)

  # Reduce once; the scatter and the curve fit both read from this so they
  # can never drift apart (see plot_mcap_binned_2()).
  binned <- all_res |>
    select(-delta) |>
    pivot_longer(-loglik) |>
    split(~name) |>
    lapply(focal_profile_points,
      diff_LL = diff_LL, min_points = min_points,
      max_diff_LL = max_diff_LL, n_bins = n_bins
    ) |>
    bind_rows(.id = "name")

  smoothed_curves <- binned |>
    split(~name) |>
    lapply(plot_mcap_binned_2, lambda = lambda) |>
    bind_rows(.id = "name") |>
    rename(value = parameter)

  ci_vals <- smoothed_curves |>
    select(name, ci_1, ci_2) |>
    distinct() |>
    pivot_longer(-name, names_to = "name2") |>
    rename(ci = value) |>
    select(-name2)

  mle_vals <- all_res |>
    select(-delta) |>
    pivot_longer(-loglik) |>
    group_by(name) |>
    slice_max(loglik) |>
    ungroup() |>
    select(name, value) |>
    rename(mle = value)

  smoothed_curves <- smoothed_curves |>
    left_join(mle_vals, by = "name") |>
    # Split onto two lines here (unlike the CSV label): "MLE [CI low, CI
    # high] (delta=...)" runs too wide for a facet panel otherwise.
    mutate(label = fmt_mle_ci(mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, delta, delta_sep = "\n"))

  smoothed_curves |>
    select(name, mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, delta) |>
    distinct() |>
    mutate(
      label = fmt_mle_ci(mle, ci_1, ci_2, ci_1_truncated, ci_2_truncated, digits = digits, include_delta = FALSE),
      parameter = parameter_labels_latex[name]
    ) |>
    arrange(factor(name, levels = param_order)) |>
    # Full-precision numeric columns (mle, ci_low/high, delta) alongside the
    # rounded `label` string, so the CSV can be reanalyzed and not just read.
    rename(ci_low = ci_1, ci_high = ci_2, ci_low_truncated = ci_1_truncated, ci_high_truncated = ci_2_truncated) |>
    select(name, parameter, mle, ci_low, ci_high, ci_low_truncated, ci_high_truncated, delta, label) |>
    write_csv(str_glue("figures/{output_prefix}_parameters_profile.csv"))

  # True MLE's raw loglik, not the noisier per-panel smoothed max.
  mle_loglik <- max(all_res$loglik, na.rm = TRUE)

  list(
    binned = binned, smoothed_curves = smoothed_curves, ci_vals = ci_vals,
    mle_vals = mle_vals, mle_loglik = mle_loglik
  )
}

#' Subtract the true MLE's log-likelihood (shared by every panel) for
#' relative-log-likelihood plotting.
apply_relative_loglik <- function(binned, smoothed_curves, mle_loglik) {
  list(
    binned = binned |> mutate(loglik = loglik - mle_loglik),
    smoothed_curves = smoothed_curves |> mutate(smoothed = smoothed - mle_loglik)
  )
}

relative_ylim <- function(binned, smoothed_curves, pad = 0.5, lower_quantile = 0.1) {
  vals <- c(binned$loglik, smoothed_curves$smoothed, 0)
  vals <- vals[is.finite(vals)]
  lo <- quantile(vals, lower_quantile, names = FALSE)
  hi <- max(vals)
  c(lo - pad, hi + pad)
}
trim_smoothed_floor <- function(binned, smoothed_curves, margin = 3) {
  bounds <- binned |>
    group_by(name) |>
    summarize(
      floor = min(loglik, na.rm = TRUE) - margin,
      ceiling = max(loglik, na.rm = TRUE) + margin,
      .groups = "drop"
    )
  smoothed_curves |>
    left_join(bounds, by = "name") |>
    filter(is.na(smoothed) | (is.na(floor) & is.na(ceiling)) |
      (smoothed >= floor & smoothed <= ceiling)) |>
    select(-floor, -ceiling)
}

plot_profile_group <- function(profile, names_subset = NULL, base_size = 22, label_size = 5,
                               relative = TRUE, ylim = NULL) {
  binned <- profile$binned
  smoothed_curves <- profile$smoothed_curves
  ci_vals <- profile$ci_vals
  mle_vals <- profile$mle_vals

  if (!is.null(names_subset)) {
    binned <- binned |> filter(name %in% names_subset)
    smoothed_curves <- smoothed_curves |> filter(name %in% names_subset)
    ci_vals <- ci_vals |> filter(name %in% names_subset)
    mle_vals <- mle_vals |> filter(name %in% names_subset)
  }

  # Facet order matches the mechanistic grouping used for the CSV tables,
  # not alphabetical. Every layer's data needs `name` as the same factor --
  # ggplot2 combines panel variables across layers, and a factor mixed with
  # plain character columns from other layers falls back to alphabetical.
  binned <- binned |> mutate(name = factor(name, levels = param_order))
  smoothed_curves <- smoothed_curves |> mutate(name = factor(name, levels = param_order))
  ci_vals <- ci_vals |> mutate(name = factor(name, levels = param_order))
  mle_vals <- mle_vals |> mutate(name = factor(name, levels = param_order))

  smoothed_curves <- trim_smoothed_floor(binned, smoothed_curves)

  y_lab <- "Log-likelihood"
  if (relative) {
    rel <- apply_relative_loglik(binned, smoothed_curves, profile$mle_loglik)
    binned <- rel$binned
    smoothed_curves <- rel$smoothed_curves
    y_lab <- "Relative log-likelihood"
    if (is.null(ylim)) ylim <- relative_ylim(binned, smoothed_curves)
  }

  # Draw the MLE point explicitly: it isn't always among `binned`'s points
  # (focal_profile_points() keeps only one point per bin).
  mle_vals <- mle_vals |> mutate(mle_y = if (relative) 0 else profile$mle_loglik)

  labels <- smoothed_curves |>
    group_by(name) |>
    summarize(label = first(label), xpos = mean(range(value)), .groups = "drop")

  p <- binned |>
    left_join(smoothed_curves |> select(name, ci_1, ci_2, delta) |> distinct(), by = "name") |>
    ggplot(aes(x = value, y = loglik)) +
    facet_wrap(~name,
      # scales = if (relative) "free_x" else "free",
      scales = "free",
      labeller = labeller(name = as_labeller(parameter_labels, label_parsed))
    ) +
    geom_point(size = 0.6, alpha = 0.4) +
    geom_line(aes(y = smoothed), data = smoothed_curves, color = okabe_ito[["blue"]], linewidth = 0.7) +
    geom_vline(aes(xintercept = mle), data = mle_vals, color = okabe_ito[["vermillion"]], linewidth = 0.5, linetype = "solid") +
    geom_point(aes(x = mle, y = mle_y), data = mle_vals, inherit.aes = FALSE, color = okabe_ito[["vermillion"]], size = 1.3) +
    geom_vline(aes(xintercept = ci), data = ci_vals, color = okabe_ito[["orange"]], linewidth = 0.5, linetype = "dashed") +
    geom_label(aes(x = xpos, y = -Inf, label = label),
      data = labels, inherit.aes = FALSE,
      hjust = 0.5, vjust = -0.3, size = label_size,
      fill = "white", alpha = 0.7, linewidth = 0,
      label.padding = unit(0.12, "lines")
    ) +
    theme_profile(base_size) +
    labs(x = "Parameter value", y = y_lab)

  # if (relative) {
  #   p <- p + coord_cartesian(ylim = ylim)
  # }
  p
}

#' Same as plot_profile_group(), but x is each parameter's estimation
#' scale -- useful for spotting a bad fit that back-transforming would mask.
plot_profile_group_transformed <- function(profile, names_subset = NULL, base_size = 22, label_size = 5,
                                           relative = TRUE, ylim = NULL) {
  binned <- profile$binned
  smoothed_curves <- profile$smoothed_curves
  ci_vals <- profile$ci_vals
  mle_vals <- profile$mle_vals

  if (!is.null(names_subset)) {
    binned <- binned |> filter(name %in% names_subset)
    smoothed_curves <- smoothed_curves |> filter(name %in% names_subset)
    ci_vals <- ci_vals |> filter(name %in% names_subset)
    mle_vals <- mle_vals |> filter(name %in% names_subset)
  }

  # Facet order matches the mechanistic grouping used for the CSV tables,
  # not alphabetical. Every layer's data needs `name` as the same factor --
  # ggplot2 combines panel variables across layers, and a factor mixed with
  # plain character columns from other layers falls back to alphabetical.
  binned <- binned |> mutate(name = factor(name, levels = param_order))
  smoothed_curves <- smoothed_curves |> mutate(name = factor(name, levels = param_order))
  ci_vals <- ci_vals |> mutate(name = factor(name, levels = param_order))
  mle_vals <- mle_vals |> mutate(name = factor(name, levels = param_order))

  smoothed_curves <- trim_smoothed_floor(binned, smoothed_curves)

  y_lab <- "Log-likelihood"
  if (relative) {
    rel <- apply_relative_loglik(binned, smoothed_curves, profile$mle_loglik)
    binned <- rel$binned
    smoothed_curves <- rel$smoothed_curves
    y_lab <- "Relative log-likelihood"
    if (is.null(ylim)) ylim <- relative_ylim(binned, smoothed_curves)
  }

  binned <- binned |> mutate(value = to_est(value, param_scale(name)))
  smoothed_curves <- smoothed_curves |>
    mutate(
      value = to_est(value, param_scale(name)),
      ci_1 = to_est(ci_1, param_scale(name)),
      ci_2 = to_est(ci_2, param_scale(name))
    )
  ci_vals <- ci_vals |> mutate(ci = to_est(ci, param_scale(name)))
  mle_vals <- mle_vals |>
    mutate(
      mle = to_est(mle, param_scale(name)),
      mle_y = if (relative) 0 else profile$mle_loglik
    )

  labels <- smoothed_curves |>
    group_by(name) |>
    summarize(label = first(label), xpos = mean(range(value)), .groups = "drop")
  facet_labels <- setNames(
    paste0(unique(binned$name), " (", param_scale(unique(binned$name)), ")"),
    unique(binned$name)
  )

  p <- binned |>
    left_join(smoothed_curves |> select(name, ci_1, ci_2, delta) |> distinct(), by = "name") |>
    ggplot(aes(x = value, y = loglik)) +
    facet_wrap(~name,
      # scales = if (relative) "free_x" else "free",
      scales = "free",
      labeller = labeller(name = facet_labels)
    ) +
    geom_point(size = 0.6, alpha = 0.4) +
    geom_line(aes(y = smoothed), data = smoothed_curves, color = okabe_ito[["blue"]], linewidth = 0.7) +
    geom_vline(aes(xintercept = mle), data = mle_vals, color = okabe_ito[["vermillion"]], linewidth = 0.5, linetype = "solid") +
    geom_vline(aes(xintercept = ci), data = ci_vals, color = okabe_ito[["orange"]], linewidth = 0.5, linetype = "dashed") +
    geom_label(aes(x = xpos, y = -Inf, label = label),
      data = labels, inherit.aes = FALSE,
      hjust = 0.5, vjust = -0.3, size = label_size,
      fill = "white", alpha = 0.7, linewidth = 0,
      label.padding = unit(0.12, "lines")
    ) +
    theme_profile(base_size) +
    labs(x = "Parameter value (estimation scale)", y = y_lab)

  if (relative) {
    p <- p + coord_cartesian(ylim = ylim)
  }
  p
}

#' Draw a parameter-group plot, print it (so it renders in the document), and
#' save it to `filename`.
save_profile_plot <- function(profile, names_subset, filename, label_size = 5, base_size = 22,
                              width = 14, height = 14, dpi = 600) {
  p <- plot_profile_group(profile, names_subset, base_size = base_size, label_size = label_size)
  print(p)
  # cairo_pdf (not the default pdf() device) is needed so the Δ glyph in
  # the panel labels embeds correctly instead of dropping out/showing a box.
  ggsave(filename, plot = p, width = width, height = height, dpi = dpi, device = cairo_pdf)
  invisible(p)
}
```

# Ahmedabad, relative humidity

```{r, fig.height = 20, fig.width = 20, eval = TRUE}
ahmedabad_rh <- analyze_profile(
  "aggregated_results/profile_Ahmedabad_hadISD_1997_2011_8_9.csv",
  output_prefix = "Ahmedabad_RH"
)

print(plot_profile_group(ahmedabad_rh, base_size = 16, label_size = 3.5))
ggsave("figures/profile_Ahmedabad_RH.pdf",
  width = 14, height = 14, dpi = 600,
device = cairo_pdf)

print(plot_profile_group_transformed(ahmedabad_rh, base_size = 12, label_size = 5))

save_profile_plot(ahmedabad_rh, param_groups$transmission, "figures/profile_Ahmedabad_RH_transmission.pdf")
save_profile_plot(ahmedabad_rh, param_groups$initial, "figures/profile_Ahmedabad_RH_initial.pdf")
save_profile_plot(ahmedabad_rh, param_groups$immunity, "figures/profile_Ahmedabad_RH_immunity.pdf")
```

# Ahmedabad, maximum temperature

```{r, fig.height = 20, fig.width = 20, eval = TRUE}
ahmedabad_temp <- analyze_profile(
  "aggregated_results/profile_Ahmedabad_Max_Temp_1997_2011_9_9.csv",
  output_prefix = "Ahmedabad_Max_Temp"
)
print(plot_profile_group(ahmedabad_temp, base_size = 16, label_size = 3.5))
ggsave("figures/profile_Ahmedabad_Max_Temp.pdf",
  width = 14, height = 14, dpi = 600,
  device = cairo_pdf
)

print(plot_profile_group_transformed(ahmedabad_temp, base_size = 12, label_size = 5))

save_profile_plot(ahmedabad_temp, param_groups$transmission, "figures/profile_Ahmedabad_Max_Temp_transmission.pdf")
save_profile_plot(ahmedabad_temp, param_groups$initial, "figures/profile_Ahmedabad_Max_Temp_initial.pdf")
save_profile_plot(ahmedabad_temp, param_groups$immunity, "figures/profile_Ahmedabad_Max_Temp_immunity.pdf")
```

# Surat, relative humidity

```{r, fig.height = 20, fig.width = 20, eval = TRUE}
surat_rh <- analyze_profile(
  "aggregated_results/profile_Surat_hadISD_1997_2016_7_7.csv",
  output_prefix = "Surat_RH"
)
print(plot_profile_group(surat_rh, base_size = 16, label_size = 3.5))
ggsave("figures/profile_Surat_RH.pdf",
  width = 14, height = 14, dpi = 600,
  device = cairo_pdf
)

print(plot_profile_group_transformed(surat_rh, base_size = 12, label_size = 5))

save_profile_plot(surat_rh, param_groups$transmission, "figures/profile_Surat_RH_transmission.pdf")
save_profile_plot(surat_rh, param_groups$initial, "figures/profile_Surat_RH_initial.pdf")
save_profile_plot(surat_rh, param_groups$immunity, "figures/profile_Surat_RH_immunity.pdf")
```

# Surat, maximum temperature

```{r, fig.height = 20, fig.width = 20, eval = TRUE}
surat_temp <- analyze_profile(
  "aggregated_results/profile_Surat_Max_Temp_1997_2016_5_9.csv",
  output_prefix = "Surat_Max_Temp"
)

print(plot_profile_group(surat_temp, base_size = 16, label_size = 3.5))
ggsave("figures/profile_Surat_Max_Temp.pdf",
  width = 14, height = 14, dpi = 600,
  device = cairo_pdf
)

print(plot_profile_group_transformed(surat_temp, base_size = 12, label_size = 5))

save_profile_plot(surat_temp, param_groups$transmission, "figures/profile_Surat_Max_Temp_transmission.pdf")
save_profile_plot(surat_temp, param_groups$initial, "figures/profile_Surat_Max_Temp_initial.pdf")
save_profile_plot(surat_temp, param_groups$immunity, "figures/profile_Surat_Max_Temp_immunity.pdf")
```
