---
title: "Plausibility of biological rates"
author: "Leonardo Souto Ferreira"
date: today
format: html
geometry:
  - margin=2cm
warning: false
message: false
echo: false
fig-width: 8
fig-height: 4
---



```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(autodep = TRUE)
proj_root <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
setwd(proj_root)
knitr::opts_knit$set(root.dir = proj_root)
pkgload::load_all(proj_root)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(sf)
library(patchwork)
library(basemaps)
library(ggspatial)
```

```{r helpers}

#' Read a profile-likelihood CSV, keep the acceptable region, get the
#' best-fitting parameter set, and particle-filter it (data-conditioned
#' hidden states, not a blind simulation) over the full study period.
fit_and_predict <- function(city, model, covariate_var, profile_file,
                            start_year, end_year, window_start, window_end,
                            end_year_prediction = 2023, n_sims = 10) {
  all_res <- read_csv(profile_file, show_col_types = FALSE)

  # Some profile files carry extra bookkeeping columns (mode/profile_var/source_file)
  # from refined profiling runs; restrict to the refined region when present.
  if ("mode" %in% names(all_res)) {
    all_res <- all_res |>
      filter(mode == "refined_second", rho >= 0.01) |>
      select(-mode, -profile_var, -source_file)
  } else {
    all_res <- all_res |> filter(rho >= 0.01)
  }

  top_params <- all_res |> get_top_sample(k = 1)

  ## predict_model_filtered() always covers the full [start_year,
  ## end_year_prediction] interval (no training/prediction split), so
  ## end_year here just anchors the covariate normalization to the window
  ## the parameters were actually fit on (actual_end_year defaults to it).
  top_params |>
    predict_model_filtered(
      n_sims = n_sims,
      model = model, covariate = covariate_var,
      start_year = start_year, start_month = 1,
      end_year = end_year, end_month = 12,
      end_year_prediction = end_year_prediction, end_month_prediction = 12,
      window_start = window_start, window_end = window_end,
      dataset = paste0("data/", city, "/dataset_", city, "_2023.csv")
    ) |>
    mutate(city = city, covariate_var = covariate_var, model = model) |>
    mutate(covariate_var = if_else(model == "baseline", "Baseline", covariate_var)) |>
    bind_cols(as.list(top_params))
}
```

## Model configurations

One row per city/covariate model, matching the training windows used in the
profile-likelihood fits. The baseline model has no climate-covariate
term, so `covariate_var`/window are only used for the (unused) preprocessing
step and are set to match that city's RH model for consistency.

```{r configs}
model_configs <- tribble(
  ~city, ~covariate_label, ~model, ~covariate_var, ~profile_file, ~start_year, ~end_year, ~window_start, ~window_end,
  "Ahmedabad", "Relative Humidity", "inf_exponent", "hadISD", "aggregated_results/profile_Ahmedabad_hadISD_1997_2011_8_9.csv", 1997, 2011, 8, 9,
  "Ahmedabad", "Maximum Temperature", "inf_exponent", "Max_Temp", "aggregated_results/profile_Ahmedabad_Max_Temp_1997_2011_9_9.csv", 1997, 2011, 9, 9,
  "Ahmedabad", "Baseline", "baseline", "hadISD", "aggregated_results/profile_Ahmedabad_baseline_1997_2011.csv", 1997, 2011, 8, 9,
  "Surat", "Relative Humidity", "inf_exponent", "hadISD", "aggregated_results/profile_Surat_hadISD_1997_2016_7_7.csv", 1997, 2016, 7, 7,
  "Surat", "Maximum Temperature", "inf_exponent", "Max_Temp", "aggregated_results/profile_Surat_Max_Temp_1997_2016_5_9.csv", 1997, 2016, 5, 9,
  "Surat", "Baseline", "baseline", "hadISD", "aggregated_results/profile_Surat_baseline_1997_2016.csv", 1997, 2016, 7, 7,
)

model_configs
```

## Fit models and simulate

```{r fit-all, cache=FALSE, dependson="helpers"}
predictions <- model_configs |>
  mutate(result = purrr::pmap(
    list(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end),
    function(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end) {
      fit_and_predict(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end)
    }
  ))

all_results <- predictions$result |>
  bind_rows() |>
  mutate(covariate_var = case_when(
    covariate_var == "hadISD" ~ "Relative Humidity",
    covariate_var == "Max_Temp" ~ "Maximum Temperature",
    TRUE ~ "Baseline"
  )) |>
  mutate(
    bH = if_else(model == "baseline", 0, bH),
    covariate = if_else(model == "baseline", 0, covariate)
  )
head(all_results)
```

## Plot palette

Shared look for the facet plots below, matching the minimal theme used
across the manuscript figures (e.g. `theme_profile()` in
`parameter_profiles.qmd`, `plot_prediction_panel()` in `new_figures.qmd`).
The training/prediction split no longer means anything for these two plots
(the models are now particle-filtered — data-conditioned, not blindly
simulated — over the full interval, see `fit_and_predict()` above), so both
plots treat all rows as one continuous series.

```{r palette}
CI <- 0.95
line_color <- "#0072B2"
ribbon_color <- "#B3D5E6"

theme_facets <- function(base_size = 12) {
  theme_minimal(base_size = base_size, base_family = "sans") +
    theme(
      axis.line = element_line(color = "black"),
      legend.position = "none",
      panel.grid.minor = element_blank(),
      text = element_text(family = "Helvetica")
    )
}
```

## Prevalence plots

```{r, dependson=c("helpers", "palette")}

all_results |>
  filter(.id != "data") |>
  mutate(.id = as.numeric(.id)) |>
  ggplot(aes(x = time, y = (S1 + S2) / (S1 + S2 + E + I2 + I1))) +
  facet_grid(cols = vars(covariate_var), rows = vars(city)) +
  ggdist::stat_lineribbon(.width = CI, linewidth = 0.7, color = line_color, fill = ribbon_color) +
  labs(x = "Time", y = "Susceptible fraction") +
  theme_facets(base_size = 16)

ggsave(here::here("figures/prevalence_plots.pdf"), width = 14)
```


## Transmission Rate plots

```{r, dependson=c("helpers", "palette")}
all_results |>
  filter(.id != "data") |>
  mutate(.id = as.numeric(.id)) |>
  mutate(beta = exp(b1 * season1 + b2 * season2 + b3 * season3 + b4 * season4 +
    b5 * season5 + b6 * season6 + season4 * bH * covariate)) |>
  group_by(city, covariate_var, time) |>
  summarize(beta = mean(beta, na.rm = TRUE), .groups = "drop") |>
  mutate(
    year = floor(time),
    month = round((time - year) * 12 + 1)
  ) |>
  ggplot(aes(x = month, y = beta, group = year)) +
  facet_grid(
    cols = vars(covariate_var), rows = vars(city),
    scales = "free_y"
  ) +
  geom_line(color = "grey70") +
  stat_summary(fun = median, geom = "line", aes(group = 1), color = line_color, linewidth = 0.7) +
  scale_x_continuous(breaks = seq(1, 12, by = 2), labels = month.abb[seq(1, 12, by = 2)]) +
  labs(x = "Month", y = "Transmission rate") +
  theme_facets(base_size = 16) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(here::here("figures/transmission_rate_plots.pdf"), width = 14)
```