---
title: "Quantitative estimates of the fits"
author: "Leonardo Souto Ferreira"
date: today
format: html
geometry:
  - margin=2cm
warning: false
message: false
echo: false
fig-width: 8
fig-height: 4
---

This document fits each city/climate-covariate model, simulates from the
fitted posterior, and scores the simulations against observed cases with the
Continuous Ranked Probability Score (CRPS). CRPS is reported separately for
the training period and for the testing (out-of-sample) period, and the
testing period is further split into before and after 2019.

```{r setup, include=FALSE, message=FALSE}
proj_root <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
setwd(proj_root)
knitr::opts_knit$set(root.dir = proj_root)
pkgload::load_all(proj_root)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(sf)
library(patchwork)
library(basemaps)
library(ggspatial)
```

```{r helpers}

#' Read a profile-likelihood CSV, keep the acceptable region, get the
#' best-fitting parameter set, simulate from it and label training vs.
#' testing (prediction) periods.
fit_and_predict <- function(city, model, covariate_var, profile_file,
                            start_year, end_year, window_start, window_end,
                            end_year_prediction = 2023, n_sims = 1000) {
  all_res <- read_csv(profile_file, show_col_types = FALSE)

  # Some profile files carry extra bookkeeping columns (mode/profile_var/source_file)
  # from refined profiling runs; restrict to the refined region when present.
  if ("mode" %in% names(all_res)) {
    all_res <- all_res |>
      filter(mode == "refined_second", rho >= 0.01) |>
      select(-mode, -profile_var, -source_file)
  } else {
    all_res <- all_res |> filter(rho >= 0.01)
  }

  all_res |>
    get_top_sample(k = 1) |>
    predict_model(city,
      n_sims = n_sims,
      model = model, covariate = covariate_var,
      start_year = start_year, start_month = 1,
      end_year = end_year, end_month = 12,
      end_year_prediction = end_year_prediction, end_month_prediction = 12,
      window_start = window_start, window_end = window_end,
      dataset = paste0("data/", city, "/dataset_", city, "_2023.csv"),
      output_format = "data.frame"
    ) |>
    mutate(city = city)
}

#' Per-time-point coverage of the simulation envelope around the observed
#' data, split into training, and testing before/after 2019 (see
#' `label_period()` below).
compute_coverage <- function(result_df) {
  result_df |>
    filter(type != "data") |>
    left_join(
      result_df |> filter(type == "data") |> select(time, observed = PF),
      by = "time"
    ) |>
    group_by(time, type) |>
    summarize(
      q025 = quantile(PF, 0.025),
      q975 = quantile(PF, 0.975),
      observed = mean(observed),
      .groups = "drop"
    ) |>
    mutate(
      in_between = between(observed, q025, q975),
      period = label_period(type, time)
    ) |>
    group_by(period) |>
    summarize(coverage = mean(in_between), n = n(), .groups = "drop")
}

#' Observed vs. median-predicted calibration plot, faceted/colored by type
#' (training vs. prediction).
plot_calibration <- function(result_df) {
  result_df |>
    filter(type != "data") |>
    left_join(
      result_df |> filter(type == "data") |> select(time, observed = PF),
      by = "time"
    ) |>
    group_by(time, type) |>
    summarize(
      median = median(PF, na.rm = TRUE),
      q025 = quantile(PF, 0.025),
      q975 = quantile(PF, 0.975),
      observed = mean(observed),
      .groups = "drop"
    ) |>
    ggplot(aes(x = observed, y = median, ymin = q025, ymax = q975, color = type)) +
    geom_abline(intercept = 0, slope = 1) +
    geom_errorbar() +
    geom_point() +
    theme_bw(12)
}

#' CRPS per time point. Returns one row per observation time, with `type`
#' ("training"/"prediction") carried over from the simulation ensemble so
#' training vs. testing periods can be identified downstream.
compute_crps <- function(result_df) {
  observed <- result_df |>
    filter(type == "data") |>
    select(time, observed = PF)

  sims <- result_df |>
    filter(type != "data") |>
    arrange(time)

  time_type <- sims |>
    distinct(time, type) |>
    arrange(time)

  pred_matrix <- sims |>
    select(time, .id, PF) |>
    pivot_wider(names_from = .id, values_from = PF) |>
    arrange(time) |>
    select(-time) |>
    as.matrix()

  observed_y <- time_type |>
    left_join(observed, by = "time") |>
    pull(observed)

  scores <- scoringRules::crps_sample(y = observed_y, dat = pred_matrix, method = "edf")

  time_type |> mutate(observed = observed_y, score = scores)
}

#' Label each CRPS observation as training, or testing before/after 2019.
label_period <- function(type, time) {
  case_when(
    type == "training" ~ "Training",
    time < 2019 ~ "Testing (pre-2019)",
    TRUE ~ "Testing (post-2019)"
  )
}
```

## Model configurations

One row per city/covariate model, matching the training windows used in the
profile-likelihood fits. The baseline model has no climate-covariate
term, so `covariate_var`/window are only used for the (unused) preprocessing
step and are set to match that city's RH model for consistency.

```{r configs}
model_configs <- tribble(
  ~city, ~covariate_label, ~model, ~covariate_var, ~profile_file, ~start_year, ~end_year, ~window_start, ~window_end,
  "Ahmedabad", "Relative Humidity", "inf_exponent", "hadISD", "aggregated_results/profile_Ahmedabad_hadISD_1997_2011_8_9.csv", 1997, 2011, 8, 9,
  "Ahmedabad", "Maximum Temperature", "inf_exponent", "Max_Temp", "aggregated_results/profile_Ahmedabad_Max_Temp_1997_2011_9_9.csv", 1997, 2011, 9, 9,
  "Ahmedabad", "Baseline", "baseline", "hadISD", "aggregated_results/profile_Ahmedabad_baseline_1997_2011.csv", 1997, 2011, 8, 9,
  "Surat", "Relative Humidity", "inf_exponent", "hadISD", "aggregated_results/profile_Surat_hadISD_1997_2016_7_7.csv", 1997, 2016, 7, 7,
  "Surat", "Maximum Temperature", "inf_exponent", "Max_Temp", "aggregated_results/profile_Surat_Max_Temp_1997_2016_5_9.csv", 1997, 2016, 5, 9,
  "Surat", "Baseline", "baseline", "hadISD", "aggregated_results/profile_Surat_baseline_1997_2016.csv", 1997, 2016, 7, 7,
)

model_configs
```

## Fit models and simulate

```{r fit-all, cache=FALSE}
predictions <- model_configs |>
  mutate(result = purrr::pmap(
    list(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end),
    function(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end) {
      fit_and_predict(city, model, covariate_var, profile_file, start_year, end_year, window_start, window_end)
    }
  ))
```

## Diagnostics by city and covariate

### Coverage

```{r coverage}
coverage_table <- predictions |>
  mutate(coverage = purrr::map(result, compute_coverage)) |>
  select(city, covariate_label, coverage) |>
  unnest(coverage) |>
  mutate(period = factor(period, levels = c("Training", "Testing (pre-2019)", "Testing (post-2019)"))) |>
  arrange(city, covariate_label, period)

head(coverage_table)
```

### Calibration plots

```{r calibration, fig.height=8}
calibration_plots <- predictions |>
  mutate(plot = purrr::pmap(list(result, city, covariate_label), function(result, city, covariate_label) {
    plot_calibration(result) + labs(title = paste(city, "-", covariate_label))
  }))

wrap_plots(calibration_plots$plot, ncol = 2)
```

## CRPS

```{r crps-all}
crps_all <- predictions |>
  mutate(crps = purrr::map(result, compute_crps)) |>
  select(city, covariate_label, crps) |>
  unnest(crps) |>
  mutate(period = label_period(type, time)) |>
  mutate(period = factor(period, levels = c("Training", "Testing (pre-2019)", "Testing (post-2019)")))

head(crps_all)
```

### CRPS over time

```{r crps-time-plot, fig.height=6}
crps_all |>
  ggplot(aes(x = time, y = score, color = covariate_label)) +
  geom_line() +
  facet_wrap(~city, ncol = 1, scales = "free_y") +
  theme_bw(12) +
  labs(x = "Time", y = "CRPS", color = "Covariate")
```

### Average CRPS by city, covariate and period

```{r crps-summary}
crps_summary <- crps_all |>
  group_by(city, covariate_label, period) |>
  summarize(crps = mean(score), n = n(), .groups = "drop") |>
  arrange(city, covariate_label, period)

crps_summary

crps_summary |>
  left_join(coverage_table) |>
  relocate(n, .after = last_col()) |>
  mutate(across(is.numeric, function(x) {
    round(x, digits = 2)
  })) |>
  write_csv(here::here("prediction_statistics.csv"))
```

```{r crps-summary-plot, fig.height=5}
crps_summary |>
  ggplot(aes(x = period, y = crps, fill = covariate_label)) +
  geom_col(position = position_dodge()) +
  facet_wrap(~city) +
  theme_bw(12) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
  labs(x = NULL, y = "Average CRPS", fill = "Covariate")
```
