---
title: "Yearly refitting Ahmedabad"
author: "Leonardo Souto Ferreira"
date: today
format: html
geometry:
  - margin=2cm
warning: false
message: false
echo: false
fig-width: 8
fig-height: 4
---



```{r, fig.width = 8, fig.height = 6, message = FALSE}
proj_root <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
setwd(proj_root)
knitr::opts_knit$set(root.dir = proj_root)
pkgload::load_all(proj_root)
library(tidyverse)
library(future.apply)
library(patchwork)

city <- "Ahmedabad"
covariate <- "hadISD"
window_start <- 8
window_end <- 9

yearly_preds <- read_csv(here::here(
  "aggregated_results/yearly_prediction_Ahmedabad_hadISD.csv"
))
```

## Panel A: coefficient in time

Median (line) and min-max range across the 10 Monte Carlo replicates (ribbon) of
the estimated scaling factor, by last year of the historical fitting window,
faceted by window length. The dashed line marks 2018, the last year before the
abrupt change in reported cases.

```{r}
panel_a <- yearly_preds |>
  ggplot(aes(x = year + 2010, y = scaled_b)) +
  facet_wrap(~window,
    ncol = 5,
    labeller = labeller(window = function(x) paste(x, "years"))
  ) +
  stat_summary(fun = median, geom = "line", linewidth = 0.5) +
  stat_summary(fun.data = median_hilow, fun.args = list(conf.int = 1), geom = "ribbon", alpha = 0.3) +
  geom_vline(
    xintercept = 2018,
    linetype = "dashed",
    linewidth = 0.6,
    color = "grey30"
  ) +
  theme_minimal(base_size = 7, base_family = "sans") +
  theme(
    axis.line = element_line(color = "black"),
    legend.position = "none",
    axis.title.y = ggtext::element_markdown(),
    plot.margin = margin(0, 0, 0, 0, "cm"),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica")
  ) +
  labs(
    x = "Last year of historical window",
    y = "Estimated scaling factor"
  ) +
  ylim(c(0, NA))

print(panel_a)
```

## Panel B: CRPS by window length

For each historical window length and each of the 10 parameter replicates, this
re-simulates the model's one-year-ahead rolling forecasts (`simulate_yearly_prediction`,
`model = "inf_exponent_scaled"`) and scores them against the observed cases with
the empirical-distribution CRPS (`scoringRules::crps_sample(method = "edf")`),
the same scoring approach used in `quantitative_estimates_fits.qmd`.

This is expensive: 13 window lengths x 10 replicates x 1000 simulations each.
Results are cached to `aggregated_results/crps_by_window_{city}_{covariate}.csv`
so re-rendering this document doesn't repeat the computation; delete that file
to force a re-run.

```{r crps-helpers}
#' CRPS per time point for one simulated replicate, using the empirical CDF
#' of the simulated ensemble (same approach as compute_crps() in
#' quantitative_estimates_fits.qmd).
compute_crps <- function(result_df) {
  observed <- result_df |>
    filter(type == "data") |>
    select(time, observed = PF)

  sims <- result_df |>
    filter(type != "data") |>
    arrange(time)

  time_type <- sims |>
    distinct(time, type) |>
    arrange(time)

  pred_matrix <- sims |>
    select(time, .id, PF) |>
    pivot_wider(names_from = .id, values_from = PF) |>
    arrange(time) |>
    select(-time) |>
    as.matrix()

  observed_y <- time_type |>
    left_join(observed, by = "time") |>
    pull(observed)

  scores <- scoringRules::crps_sample(y = observed_y, dat = pred_matrix, method = "edf")

  time_type |> mutate(observed = observed_y, score = scores)
}

#' Simulate one (window, replicate) parameter set's one-year-ahead rolling
#' forecasts and score the prediction period (>= 2012) against observed cases.
simulate_and_score <- function(params, prediction_window, city, covariate,
                               window_start, window_end, n_sims = 1000) {
  dat_df <- str_glue("data/{city}/dataset_{city}_2023.csv")

  result <- params |>
    simulate_yearly_prediction(
      city = city,
      n_sims = n_sims,
      model = "inf_exponent_scaled", covariate = covariate,
      start_year = 1997, start_month = 1,
      end_year = 2011, end_month = 12,
      end_year_prediction = 2023, end_month_prediction = 12,
      prediction_window = prediction_window,
      window_start = window_start, window_end = window_end,
      dataset = dat_df, output_format = c("data.frame", "pomps"), ignore_covid = TRUE,
      actual_end_year = 2011, actual_end_month = 12
    )

  training <- result$training$training |>
    mutate(type = if_else(.id == "data", "data", "training"))
  prediction <- result$prediction |>
    bind_rows() |>
    mutate(type = if_else(.id == "data", "data", "prediction"))

  complete_data <- result$complete_data |>
    select(time, PF) |>
    mutate(type = "data")

  sim_df <- bind_rows(training, prediction) |>
    select(time, .id, PF, type) |>
    filter(type != "data", time >= 2012) |>
    bind_rows(complete_data |> filter(time >= 2012)) |>
    arrange(time, type)

  compute_crps(sim_df)
}
```

```{r crps-compute}
crps_cache_file <- here::here(str_glue("aggregated_results/crps_by_window_{city}_{covariate}.csv"))

if (file.exists(crps_cache_file)) {
  crps_by_window <- read_csv(crps_cache_file)
} else {
  window_lengths <- sort(unique(yearly_preds$window))

  crps_by_window <- map_dfr(window_lengths, function(w) {
    yearly_preds |>
      filter(window == w) |>
      split(~rep) |>
      imap_dfr(function(params, rep_id) {
        simulate_and_score(params,
          prediction_window = w, city = city, covariate = covariate,
          window_start = window_start, window_end = window_end
        ) |>
          mutate(rep = rep_id)
      }) |>
      mutate(window = w)
  })

  write_csv(crps_by_window, crps_cache_file)
}

head(crps_by_window)
```

```{r crps-summary}
crps_summary <- bind_rows(
  crps_by_window |>
    filter(time < 2019) |>
    group_by(window, rep) |>
    summarize(crps = mean(score, na.rm = TRUE), .groups = "drop") |>
    group_by(window) |>
    summarize(sd = sd(crps), crps = mean(crps), .groups = "drop") |>
    mutate(includes = "Excludes 2019-2023"),
  crps_by_window |>
    filter(floor(time) != 2020) |>
    group_by(window, rep) |>
    summarize(crps = mean(score, na.rm = TRUE), .groups = "drop") |>
    group_by(window) |>
    summarize(sd = sd(crps), crps = mean(crps), .groups = "drop") |>
    mutate(includes = "Includes 2019-2023")
) |>
  mutate(includes = factor(includes, levels = c("Includes 2019-2023", "Excludes 2019-2023")))

panel_b <- crps_summary |>
  ggplot(aes(x = window, y = crps, ymin = crps - sd, ymax = crps + sd)) +
  facet_wrap(~includes) +
  geom_point() +
  geom_pointrange() +
  theme_minimal(base_size = 7, base_family = "sans") +
  theme(
    axis.line = element_line(color = "black"),
    legend.position = "none",
    axis.title.y = ggtext::element_markdown(),
    plot.margin = margin(0, 0, 0, 0, "cm"),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica")
  ) +
  labs(x = "Historical window length", y = "CRPS") +
  xlim(c(2, 14))

print(panel_b)
```

## Combined figure

```{r figure4}
(panel_a / panel_b) + plot_layout(heights = c(1, 1)) + plot_annotation(tag_levels = "A") &
  theme(plot.tag.position = c(0.01, 0.97))

ggsave(here::here("figures/figure4.pdf"), units = "mm", width = 180, height = 120, dpi = 1000)
```
